timesliced_random_cell_selection

### 2018-11-02 src/raster_sjl.Rmd
searching through year and month to add correct data...

The next piece of data we need is the observation data itself. I've sent you the observations.csv in the email with this code.
```{r}
obs <- read.csv("../data/observations3.csv", header = TRUE) #change this path to your .csv location
head(obs)
```
A note about obs$depth. This is not a measurement, but relates to the layer in the raster bricks. E.G. the observation in row one was found at rasbr[[15]], the observation in row 3 at rasbr[[17]]. I created this field myself.

@@

let's get the values manually
```{r}
testrow1 <- read.csv("../data/row1.csv", header = TRUE)
testrow1xy <- testrow1[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow1sp <- SpatialPointsDataFrame(coords = testrow1xy, data = testrow1, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow1sp
test15 <- extract(x=rasbr_aea[[15]], y = testrow1sp)
test15
testrow2 <- read.csv("../data/row1.csv", header = TRUE)
testrow2xy <- testrow2[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow2sp <- SpatialPointsDataFrame(coords = testrow2xy, data = testrow2, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow2sp
test22 <- extract(x=rasbr_aea[[22]], y = testrow2sp)
test22
testrow3 <- read.csv("../data/row1.csv", header = TRUE)
testrow3xy <- testrow3[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow3sp <- SpatialPointsDataFrame(coords = testrow3xy, data = testrow3, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow3sp
test17 <- extract(x=rasbr_aea[[17]], y = testrow3sp)
test17
```

row 1 (dpeth 15) should be 32.8761...
row 2 (depth 22) should be 33.10022...
row 3 (depth 17) should be 32.90343...

@@

Ok next step, can you dynamically name the column with the variable in question (or at least the name of the original netcdf)

>>>>

The next piece of data we need is the observation data itself. I've sent you the observations.csv in the email with this code.
```{r}
obs <- read.csv("../data/observations3.csv", header = TRUE) #change this path to your .csv location
obs$month <- sprintf("%02d",obs$month) # new addition to add the 0 infront of single digit... test for seeing if you can match the netcdf name for year month selection of bricks
head(obs)

```
A note about obs$depth. This is not a measurement, but relates to the layer in the raster bricks. E.G. the observation in row one was found at rasbr[[15]], the observation in row 3 at rasbr[[17]]. I created this field myself.

@@

let's get the values manually at depth
```{r}
testrow1 <- read.csv("../data/row1.csv", header = TRUE)
testrow1xy <- testrow1[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow1sp <- SpatialPointsDataFrame(coords = testrow1xy, data = testrow1, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow1sp
test15 <- extract(x=rasbr_aea[[15]], y = testrow1sp)
test15
testrow2 <- read.csv("../data/row1.csv", header = TRUE)
testrow2xy <- testrow2[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow2sp <- SpatialPointsDataFrame(coords = testrow2xy, data = testrow2, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow2sp
test22 <- extract(x=rasbr_aea[[22]], y = testrow2sp)
test22
testrow3 <- read.csv("../data/row1.csv", header = TRUE)
testrow3xy <- testrow3[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow3sp <- SpatialPointsDataFrame(coords = testrow3xy, data = testrow3, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow3sp
test17 <- extract(x=rasbr_aea[[17]], y = testrow3sp)
test17
```

row 1 (depth 15) should be 32.8761...
row 2 (depth 22) should be 33.10022...
row 3 (depth 17) should be 32.90343...

let's get the values manually at the surface
```{r}
testrow1.1 <- extract(x=rasbr_aea[[1]], y = testrow1sp)
testrow1.1
testrow2.1 <- extract(x=rasbr_aea[[1]], y = testrow2sp)
testrow2.1
testrow3.1 <- extract(x=rasbr_aea[[1]], y = testrow3sp)
testrow3.1
```

@@

test with just extracting the surface layer data..

```{r}
for (i in 1:length(obssp)) {  # CYCLES THROUGH THE ROWS
  obssp$testsurface[i] <- extract(x=rasbr_aea[[1]], y = obssp) #this is the equation you will be calculating for every value of y
  print(i)
  }
obssp$testsurface
obssp
```

scrap the variable name matching idea (instead just make a loop for each variable, and each variable held in a different folder). just try select by year and month.
note you have changed the dates on the .csv file so reload it

```{r warning=FALSE}
netcdf_list <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf) {
  print(netcdf_name[i]) #this just prings the name of the netCDF R is working on
  brkyr <- sapply(strsplit(netcdf_name[i], "_"), "[[", 1) # here I am extracting the first part of the filename deliminated with _ (which is the year)
  brkmth <- sapply(strsplit(netcdf_name[i], "_"), "[[", 2) # here I am extracting the second part of the filename deliminated with _ (which is the month)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) #aea is an existing raster in the projection I want that I created (environmental_data_preperation)
    for (j in 1:length(obssp)) {  # CYCLES THROUGH THE ROWS
      yr <- obssp$year[j]
      mth <- obssp$month[j]
      if (brkyr == yr &  brkmth == mth){
        de <- obssp$depth[[j]]  #have a variable for the depth layer
        obssp$samtest[j] <- extract(x=temp_brick[[de]], y = obssp) #this is the equation you will be calculating for every value of y
        obssp$samtesttop[j] <- extract(x=temp_brick[[1]], y = obssp) #this is the equation you will be calculating for every value of y
        print(j)
      }
    }
}
obssp$samtesttop
```
